Estimating dark matter halo concentration using the integrated mass profile

### 2015-11-14 paper/paper.tex
minor changes

\begin{abstract}
We present a new algorithm to estimate the concentration of N-body
dark matter halos.
The method uses the integrated mass profile to find the optimal
concentration value. 
Its main advantage is that it uses the full particle information
without any binning, making it realiable in  cases when low numerical
resolution becomes a limitation for other methods.  
Additionally, the algorithm is straightforward to implement.  
We test the performance of this method by estimating halo
concentration both on mock and N-body halos. 
We compare these results against two other methods:
maximum radial velocity measurements and radial particle binning to
fit the density profile. 
Tests on  the mock halos show that the accuracy of our method to recover input
concentrations varies with halo resolution, outperforming the other
two methods. For halos
sampled with $20$ particles our method recovers the input
concentration with $10\%$ accuracy, while for the maximum radial
velocity method it is on the order of $20\%$ 
and density profile methods fail at the $100\%$ level.
For halos with $2\times 10^4$ particles our method achieves a recovery
accuracy of $0.01\%$ while the velocity and density profile methods
achieve $0.1\%$ and $1\%$, respectively. 
We also measure the mass-concentration relationship on N-body
data. We find that within the probed mass range ($10^{12}\hMsun <
10^{14}\hMsun$) the three methods give consistent results within the
statistical uncertainties.   
We only find a small discrepancy at low masses, $M<10^{13}\hMsun$, where
our method yields lower median concentration values by $15\%-20\%$
compared to the velocity and density methods. 
From these results we believe that the new method is promising tool
to probe the internal structure of dark matter halos.
\end{abstract}

>>>>

\begin{abstract}
We present a new algorithm to estimate the concentration of N-body
dark matter halos.
The method uses the integrated mass profile to find the optimal
concentration value. 
Its main advantage is that it uses the full particle information
without any binning, making it realiable in  cases when low numerical
resolution becomes a limitation for other methods.  
Additionally, the algorithm is straightforward to implement.  
We test the performance of this method by estimating halo
concentration both on mock and N-body halos. 
We compare these results against two other methods:
maximum radial velocity measurements and radial particle binning to
fit the density profile. 
Tests on the mock halos show that the accuracy of our method to recover input
concentrations varies with halo resolution, outperforming the other
two methods. 
For halos sampled with $20$ particles our method recovers the input
concentration with $10\%$ accuracy, while for the maximum radial
velocity method it is on the order of $20\%$ and density profile
methods fail at the $100\%$ level. 
For halos with $2\times 10^4$ particles our method achieves a recovery
accuracy of $0.01\%$ while the velocity and density profile methods
achieve $0.1\%$ and $1\%$, respectively. 
We also measure the mass-concentration relationship on N-body
data. 
We find that in the probed mass range ($10^{12}\hMsun <
10^{14}\hMsun$) the three methods give consistent results within the
statistical uncertainties.   
We only find a small discrepancy at low masses, $M<10^{13}\hMsun$, where
our method yields lower median concentration values by $15\%-20\%$
compared to the velocity and density methods. 
From these results we believe that the new method is a promising tool
to probe the internal structure of dark matter halos.
\end{abstract}
